A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-28 main.Rmd
checked typos
possibly dplyr v0.8.0 will not have performance issue for date-times

A new temporal data class is needed in the upstream of the workflow, which could incorporate all the downstream modules. A relatively new R package **tibbletime** [@R-tibbletime] proposed a data class of *time tibble* to represent temporal data in heterogeneous tabular format. It only requires an index variable to declare a temporal data object, thus placing it at the import stage. However, this is a loosely defined structure, and insufficient for time series analytics and models. Because it neglects to describe observational units or entities over time, which forms a key component of time series data.

@@

The authors would like to thank Mitchell O'Hara-Wild for many discussions on the software development and Davis Vaughan for contributing ideas on rolling window functions. This article was created with knitr [@knitr] and R Markdown [@rmarkdown]. The project's Github repository <https://github.com/earowang/paper-tsibble> houses all materials required to reproduce this article and a history of the changes. To produce the analysis results as described in Section \autoref{sec:cases}, we require the **tsibble** package (`v0.6.2`) and the **dplyr** package (`v0.7.8`) installed.

>>>>

A new temporal data class is needed in the upstream of the workflow, which could incorporate all the downstream modules. A relatively new R package **tibbletime** [@R-tibbletime] proposed a data class of *time tibble* to represent temporal data in heterogeneous tabular format. It only requires an index variable to declare a temporal data object, thus placing it at the import stage. However, this is a loosely defined structure, and insufficient for time series analytics and models. Because it neglects to describe observational units or entities over time, which form a key component of time series data.

@@

The authors would like to thank Mitchell O'Hara-Wild for many discussions on the software development and Davis Vaughan for contributing ideas on rolling window functions. This article was created with knitr [@knitr] and R Markdown [@rmarkdown]. The project's Github repository <https://github.com/earowang/paper-tsibble> houses all materials required to reproduce this article and a history of the changes. <!-- To produce the analysis results as described in Section \autoref{sec:cases}, we require the **tsibble** package (`v0.6.2`) and the **dplyr** package (`v0.7.8`) installed. -->
